%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{changepage}
\usepackage{ragged2e}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  \textbf{\Huge \scshape Yeyang (Justin) Sun} \\ \vspace{1pt}
  \small \href{mailto:sunjustin969@gmail.com}{\underline{sunjustin969@gmail.com}} $|$
  \href{https://github.com/jsun969}{\underline{github.com/jsun969}} $|$
  \href{https://linkedin.com/in/jsun969}{\underline{linkedin.com/in/jsun969}} $|$
  \href{https://jsun.lol}{\underline{jsun.lol}}
\end{center}


%-----------Introduction-----------
\section{Introduction}
\justifying
\begin{adjustwidth}{8pt}{8pt}
  As a university student deeply passionate about programming, I began self-teaching full-stack development in high school. Through this experience, I honed my ability to design and implement efficient, scalable, and maintainable software systems. Actively engaging with the open-source community, I continuously enhance my skills and champion collaborative development. My fascination with exploring cutting-edge technologies drives my research endeavours. Eager to leverage my technical prowess within a dynamic team, I am committed to advancing my programming expertise and contributing to impactful projects.
\end{adjustwidth}
\raggedright

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Adelaide}{Adelaide, SA}
{Bachelor of Information Technology}{Feb. 2024 -- Nov. 2026}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Open Source Officer}{Mar. 2024 -- Present}
{University of Adelaide Computer Science Club}{Adelaide, Australia}
\resumeItemListStart
\resumeItem{Manage and contribute to open-source projects}
\resumeItem{Promote open-source culture within the club}
\resumeItem{Plan workshops and events related to open-source}
\resumeItemListEnd

\resumeSubheading
{Full Stack Engineer Intern}{July 2023 -- Nov. 2023}
{Zolplay}{Remote, China}
\resumeItemListStart
\resumeItem{Build an online game isthat.ai to promote the company's brand}
\resumeItem{Gained insights into the company's development}
\resumeItem{Help company analyze website views and user interactions}
\resumeItem{Assisted in resolving technical issues on the company's e-commerce platform}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Computer Science Club Website} $|$ \emph{TypeScript, Next.js, React, Tailwind CSS}}{Jan. 2024 -- Present}
\resumeItemListStart
\resumeItem{Build pages including events, sponsors, contact}
\resumeItem{Improve DX and UX by using cutting-edge technologies (e.g. React Server Components, React Hook Form)}
\resumeItem{Integrate database ORM and help working on backend}
\resumeItem{Design and implement an interesting easter egg}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{isthat.ai} $|$ \emph{TypeScript, Next.js, React, Tailwind CSS, Framer Motion, Drizzle ORM}}{July 2023 -- Oct. 2023}
\resumeItemListStart
\resumeItem{Build a whole online game from scratch}
\resumeItem{Implement seamless user interactions and animations by using Framer Motion}
\resumeItem{Improve user experience by optimizing website performance}
\resumeItem{Optimize SEO to enhance the shareability of user results on social media}
\resumeItem{Analyze user interactions and website views}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Jsun Dot LOL} $|$ \emph{TypeScript, Astro}}{Jan. 2023 -- Present}
\resumeItemListStart
\resumeItem{Design and build this personal website}
\resumeItem{Optimize website performance and SEO}
\resumeItem{Implement a blog system with markdown support}
\resumeItem{Integrate GitHub discussion for blog comments}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Message Pigeon} $|$ \emph{React, Nest.js, Tauri, Prisma ORM, Vue, Electron, Express.js}}{Mar. 2021 -- May 2022}
\resumeItemListStart
\resumeItem{Implement a notification system with real-time updates by using WebSocket}
\resumeItem{Learn how to build a full-stack application from scratch}
\resumeItem{Present this project as a teaching resource in high school and received high praise from the teachers}
\resumeItem{Implement a software with GUI by using Tauri/Electron}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------Open Source Contributions-----------
\section{Open Source Contributions}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{react-hook-form-antd}}{Apr. 2023 -- Present}
\resumeItemListStart
\resumeItem{A library that integrates React Hook Form with Ant Design}
\resumeItem{Gain over 1000 downloads per week on NPM}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Astro}}{Feb. 2023}
\resumeItemListStart
\resumeItem{Integrate Vercel Analytics}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{React Hook Form}}{June 2022 -- Aug. 2022}
\resumeItemListStart
\resumeItem{Implement a browser extension for the library to help developers debug their forms}
\resumeItem{Integrate AJV to validate form data}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages: }{TypeScript, JavaScript, SQL, C/C++, Python} \\
        \textbf{Frameworks: }{React, Next.js, Astro, React Native, Nest.js, Vue} \\
        \textbf{Developer Tools: }{Git, VS Code, ESLint, Prettier, NPM/PNPM} \\
        \textbf{Libraries: }{React Hook Form, Framer Motion, Tailwind CSS, TRPC, Prisma ORM, Drizzle ORM, Ant Design, MUI}
        }}
\end{itemize}


%-----------Appreciation-----------
\section{Appreciation}
\justifying
\begin{adjustwidth}{8pt}{8pt}
  Thank you for reviewing my resume. I am enthusiastic about the prospect of working with your team and contributing to your company's goals.
\end{adjustwidth}
\raggedright

%-------------------------------------------
\end{document}